Iroko: Predictive Datacenter Congestion Control

### 2017-12-12 Documents/Report/intro.tex
Minor fixes

Developments in the past decade have changed the general networking 
environment. Data centers have emerged as an exciting new research frontier, 
posing novel design challenges and opportunities. Driven by minimization of 
costs and maximization of compute power, data centers must run at the highest 
possible utilization to achieve the ideal compute/cost ratio.
Optimizing the distribution of traffic and simultaneously guaranteeing fairness 
is a perennial challenge for any network operator.
Inefficient routing and congestion control can quickly lead to 
bufferbloat~\cite{bufferbloat} and the eventual collapse of a high-load 
network, requiring more sophisticated solutions. In fact, recent insights into 
datacenter network traffic have shown that buffer overruns and small 
short-lived bursts are the primary factor of loss.\cite{fb_dc,msr_dc,dctcp}

@@

TCP's algorithm is a best-effort solution to globally maximize utilization 
under the fairness principle. While this design has not fundamentally changed 
over the last thirty years, new research advancements raise the question if TCP 
is still the most reliable option.~\cite{pcc,bbr,perc}

>>>>

Developments in the past decade have changed the general networking 
environment. Data centers have emerged as an exciting new research frontier, 
posing novel design challenges and opportunities. Driven by minimization of 
costs and maximization of compute power, they must run at the highest 
possible utilization to achieve the ideal compute/cost ratio.

Optimizing the distribution of traffic and simultaneously guaranteeing fairness is a perennial challenge for any network operator.
Inefficient routing and congestion control can quickly lead to 
bufferbloat~\cite{bufferbloat} and the eventual collapse of a high-load 
network, requiring more sophisticated solutions. In fact, recent insights into 
datacenter network traffic have shown that buffer overruns and small 
short-lived bursts are the primary factor of loss.\cite{fb_dc,msr_dc,dctcp}

@@

TCP's algorithm is a best-effort solution to globally maximize utilization 
under the fairness principle. This design has not fundamentally changed 
over the last thirty years, and new research advancements raise the question if TCP can still be considered to be the most sensible option.~\cite{pcc,bbr,perc}
